Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup

### 2013-07-02 snapshot_system/failover.tex
Updated vo-fsb-links figure to use shuffled vm list.
revisions

Figure~\ref{fig-vo-links} shows the average number of VMs sharing a block in
the global index as more VMs are added in VO.  The first 15 VMs are all windows
machines, so that explains the initial higher values, but for the most part the
average number of links is between 1.5 and 2. Figure~\ref{fig-vo-fsb-links}
shows the average number of VMs sharing a filesystem block (FSB) in the global
The first 15 VMs added are all windows (though the last one has a much larger
hard drive which explains the drop after 14), which is why the number of block
links goes up quickly for the first half of the graph. You can see in the plot
that even though a FSB contains 16K chunks, the average number of links to an
FSB is only several times the number of average links to a chunk. This is
because even in the VO global deduplication model, as long as writes are
batched a single FSB will tend to contain chunks from only a small number of
VMs. Below we show the significant impact the number of links has on VM backup
reliability.

@@

in our current testbed we have measured the average number of links
per block (Figure~\ref{vo-links}) and number of links per chunk (Figure~\ref{fig-vo-fsb-links})
in our dataset. For the complete dataset, we also found the average number of links to CDS chunks, which
was 11 using a 5\% CDS. From Figure~\ref{fig-vo-fsb-links} you can see that as you add VMs, the average
number of links to a chunk increases. We expect that this trend will level out with larger datasets, but
should continue to increase at a slower rate. 
For the VC model, we have to consider both CDS chunks and 
Non-CDS chunks. In the VO model all data is shared, but in VC only the CDS data is shared, but at a much
higher rate. This gives a strong advantage to VC, in that for a large percent of the data (95-99\%), there
is only one VM pointing to each Non-CDS chunk. You can see the increase in reliability in Figure~\ref{fig-vm-availability}.
}

>>>>

Figure~\ref{fig-vo-links} shows the average number of VMs sharing a block in
the global index as more VMs are added in VO. The first 15 VMs are all windows
machines in that plot, so that explains the initial higher values, but for the
most part the average number of links is between 1.5 and 2.
Figure~\ref{fig-vo-fsb-links} shows the average number of VMs sharing a
filesystem block (FSB) in the global index as VMs are added. Two of the VMs had
much larger hard drives (\~300GB), which explains the 2 drops, as those two VMs
added much more unique data than normal. You can see in the plot that even
though a FSB contains 16K chunks, the average number of links to an FSB is only
several times the number of average links to a chunk. This is because even in
the VO global deduplication model, as long as writes are batched a single FSB
will tend to contain chunks from only a small number of VMs. Below we show the
significant impact the number of links has on VM backup reliability.

@@

in our current testbed we have measured the average number of links per block
(Figure~\ref{vo-links}) and number of links per chunk
(Figure~\ref{fig-vo-fsb-links}) in our dataset. For the complete dataset, we
also found the average number of links to CDS chunks, which was 11 using a 5\%
CDS. From Figure~\ref{fig-vo-fsb-links} you can see that as you add VMs, the
average number of links to a chunk increases linearly for our dataset. We
expect that this trend will level out with larger datasets, but should continue
to increase at a slower rate.  For the VC model, we have to consider both CDS
chunks and Non-CDS chunks. In the VO model all data is shared, but in VC only
the CDS data is shared, but at a much higher rate. This gives a strong
advantage to VC, in that for a large percent of the data (95-99\%), there is
only one VM pointing to each Non-CDS chunk. You can see the increase in
reliability in Figure~\ref{fig-vm-availability}.
}

### 2013-07-02 snapshot_system/intro.tex
revisions

This paper seeks for a low-cost architecture option  that collocates
a backup service with other cloud services and  uses a minimum amount of resources. 
%Since most of backup data is not used in practice, system resource in such a service is not fully utilized.
%The dirty bit approach~\cite{??}  which checks the version difference can effectively remove
%duplicates while using content fingerprints can significantly compress more~\cite{Bottlneck08}.
%On the other hand, comparing fingerprints  adds significant  memory cost. 
%Since each physical machine in a cluster  hosts many VMs, memory contention happens frequently.
%Cloud providers often wish that the backup service only consumes  small or modest resources
%with a minimal impact to the existing cloud services.  
%We study and evaluate the integration of several deduplication strategies to meet
%the low-cost collocation requirement. 
%A recent study using subsampling~\cite{Guo2011}  can significantly reduce the memory requirement.
We also consider the fact that after
deduplication most data chunks are shared by several to many virtual machines.
Failure of shared data chunks can have a catastrophic effect and many
snapshots of virtual machines would be affected.
The previous work in deduplication focuses on the efficiency and approximation of
finger print comparison, and has not addressed fault tolerance together with deduplication.
Thus we also seek deduplication options that yield better fault isolation.
% along with a low-cost solution.
Another issue considered is that
that deletion of old snapshots compete for computing resource as well. That is because data dependence created
deletion of old snapshots compete for computing resources as well so deletion needs
to be considered in system design. The additional complexity for deletions
come from the dependencies created by multiple links to the same problem, so
some solution is needed to determine blocks with no dependent snapshots after deletion.
especially when  VMs can migrate around in the cloud.

@@

The paper studies and evaluates  an integrated approach which uses  multiple duplicate detection strategies
based on  version  detection, inner VM duplicate search,
and controlled cross-VM comparison. 
This approach is VM centric by localizing duplicate detection within each VM  
and by packaging data chunks from the same VM into a file system block as much as possible.
By narrowing duplicate sharing within a small amount of data chunks,
this scheme can afford to allocate extra replicas of these shared chunks for better
fault resilience.
Localization also brings the benefits of parallelism exploitation so
backup operations can run simultaneously without a central  bottleneck.
This  VM-centric solution uses  a small amount of  memory while delivering a decent deduplication efficiency. 
%Our deletion strategy uses a double Bloom filter strategy for periodic mark-and-sweeping of expired data.
We have developed a prototype system that runs a cluster of Linux machines with Xen.
The backup storage uses a standard distributed file system with data replication and block packaging.
%and we allocate more  replicas for the commonly-shared  data 
%blocks among VM snapshots to enhance fault tolerance.

>>>>

This paper seeks for a low-cost architecture option  that collocates
a backup service with other cloud services and  uses a minimum amount of resources. 
%Since most of backup data is not used in practice, system resource in such a service is not fully utilized.
%The dirty bit approach~\cite{??}  which checks the version difference can effectively remove
%duplicates while using content fingerprints can significantly compress more~\cite{Bottlneck08}.
%On the other hand, comparing fingerprints  adds significant  memory cost. 
%Since each physical machine in a cluster  hosts many VMs, memory contention happens frequently.
%Cloud providers often wish that the backup service only consumes  small or modest resources
%with a minimal impact to the existing cloud services.  
%We study and evaluate the integration of several deduplication strategies to meet
%the low-cost collocation requirement. 
%A recent study using subsampling~\cite{Guo2011}  can significantly reduce the memory requirement.
We also consider the fact that after
deduplication most data chunks are shared by several to many virtual machines.
Failure of shared data chunks can have a catastrophic effect and many
snapshots of virtual machines would be affected.
The previous work in deduplication focuses on the efficiency and approximation of
finger print comparison, and has not addressed fault tolerance together with deduplication.
Thus we also seek deduplication options that yield better fault isolation.
% along with a low-cost solution.
Another issue considered is that
that deletion of old snapshots compete for computing resource as well. That is because data dependence created
deletion of old snapshots competes for computing resources as well so deletion needs
to be considered in system design. The additional complexity for deletions
come from the dependencies created by multiple links to the same problem, so
some solution is needed to determine blocks with no dependent snapshots after deletion.
especially when  VMs can migrate around in the cloud.

@@

The paper studies and evaluates  an integrated approach which uses  multiple duplicate detection strategies
based on  version  detection, inner VM duplicate search,
and controlled cross-VM comparison. 
This approach is VM centric by localizing duplicate detection within each VM  
and by packaging data chunks from the same VM into a file system block as much as possible.
By narrowing duplicate sharing within a small percent of data chunks,
this scheme can afford to allocate extra replicas of these shared chunks for better
fault resilience.
Localization also brings the benefits of greater ability to exploit parallelism so
backup operations can run simultaneously without a central  bottleneck.
This  VM-centric solution uses  a small amount of  memory while delivering a reasonable deduplication efficiency. 
%Our deletion strategy uses a double Bloom filter strategy for periodic mark-and-sweeping of expired data.
We have developed a prototype system that runs a cluster of Linux machines with Xen.
The backup storage uses a standard distributed file system with data replication and block packaging.
%and we allocate more  replicas for the commonly-shared  data 
%blocks among VM snapshots to enhance fault tolerance.
